Supplementary Information for:

### 2017-07-12 supp/supp.Rmd
add code_folding

---
title: "Supplementary Information for:"
subtitle: A simplified dynamic bioenergetic model for coral-*Symbiodinium* symbioses and coral bleaching as an alternate stable state
author: "Ross Cunning, Erik B. Muller, Ruth D. Gates, Roger M. Nisbet"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 1
bibliography: library.bib
---

@@

#### $K_X$: Half-saturation constant of assimilation from host feeding {-}
For consistency, and due to a lack of available data, we use the same value as @Muller:2009io:  
```{r KX}
1e-6
```
C-mol X L^-1^
<br><br>

@@

#### $y_{C}$: Yield of biomass formation from photosynthate {-}
This coefficient specifies the efficiency of conversion of photosynthate into biomass at the biomass synthesizing units, which combine photosynthate (CH~2~O), ammonia (NH~3~) and O~2~ to form biomass, water, and CO~2~. Because of thermodynamic constraints, there is an energetic overhead on converting carbon into biomass. In order to balance this macrochemical equation, there must be a carbon loss, which is accounted for using $y_{C}$ < 1. We take a value of 0.8 following @Muller:2009io:

@@

#### $j_{SGm}$: Maximum specific growth rate of symbiont {-}
We use the maximum specific growth rate of *Symbiodinium* that is reported by @Chang:1983p8066:  
```{r jSGm, echo=F}
0.25
```
C-mol S C-mol S^-1^ d^-1^
<br><br>

>>>>

---
title: "Supplementary Information for:"
subtitle: A simplified dynamic bioenergetic model for coral-*Symbiodinium* symbioses and coral bleaching as an alternate stable state
author: "Ross Cunning, Erik B. Muller, Ruth D. Gates, Roger M. Nisbet"
output:
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
    toc_depth: 1
bibliography: library.bib
---

@@

#### $K_X$: Half-saturation constant of assimilation from host feeding {-}
For consistency, and due to a lack of available data, we use the same value as @Muller:2009io :  
```{r KX}
1e-6
```
C-mol X L^-1^
<br><br>

@@

#### $y_{C}$: Yield of biomass formation from photosynthate {-}
This coefficient specifies the efficiency of conversion of photosynthate into biomass at the biomass synthesizing units, which combine photosynthate (CH~2~O), ammonia (NH~3~) and O~2~ to form biomass, water, and CO~2~. Because of thermodynamic constraints, there is an energetic overhead on converting carbon into biomass. In order to balance this macrochemical equation, there must be a carbon loss, which is accounted for using $y_{C}$ < 1. We take a value of 0.8 following @Muller:2009io :

@@

#### $j_{SGm}$: Maximum specific growth rate of symbiont {-}
We use the maximum specific growth rate of *Symbiodinium* that is reported by @Chang:1983p8066 :  
```{r jSGm, echo=F}
0.25
```
C-mol S C-mol S^-1^ d^-1^
<br><br>
